Live Functional Programming with Typed Holes

### 2018-04-16 intro.tex
reorder sentence for flow

Moreover, we need to be able to run programs containing not only expression holes but also type holes.
In the static semantics developed by \citet{popl-paper}, we derive the machinery for 
reasoning statically about type holes from gradual type theory, 
identifying the type hole with the unknown type \cite{DBLP:conf/snapl/SiekVCB15,Siek06a}. 
To specify our intended dynamic semantics for incomplete programs, then, we can look to the dynamic semantics from
gradual type theory, which selectively inserts dynamic casts as necessitated by missing type information to maintain type safety. 
%However, this \IS again somewhat dissatisfying from the perspective of live programming because when a cast fails, evaluation again stops with 
However, when a cast fails, evaluation again stops with 
an exception.
%
As a result, traditional gradual typing approaches still leave the live programming environment unable to provide feedback about the parts 
of the program that do not depend on the problematic sub-expression (e.g. later cells in a lab notebook).

>>>>

Moreover, we need to be able to run programs containing not only expression holes but also type holes.
The static semantics developed by \citet{popl-paper} derives the machinery for 
reasoning statically about type holes from gradual type theory, 
identifying the type hole with the unknown type \cite{DBLP:conf/snapl/SiekVCB15,Siek06a}.
%
As such, we can look to the dynamic semantics from
gradual type theory to specify the dynamic semantics for incomplete programs,
which selectively inserts dynamic casts as necessitated by missing type information to maintain type safety. 
%However, this \IS again somewhat dissatisfying from the perspective of live programming because when a cast fails, evaluation again stops with 
However, when a cast fails, evaluation again stops with 
an exception.
%
As a result, traditional gradual typing approaches still leave the live programming environment unable to provide feedback about the parts 
of the program that do not depend on the problematic sub-expression (e.g. later cells in a lab notebook).
